Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-23 VMCAI-revised-version/final.tex
appendix minsky

\mathieu{Reviewer 1: the example at the bottom of \textbf{ page~\pageref{indec WSTS}}, even if it is a WSTS, is a very particular case [...] wonder if classes containing such  systems are interesting per se. }

@@

We now consider the case $\Safe = \mathop{\downarrow} \Safe$.
%
Unfortunately {\sc State-resilience} is undecidable in this case. As for {\sc Resilience} in WSTS when $\Safe = \mathop{\downarrow} \Safe$, this stems from undeciability of the corresponding problem in Minsky machines.
Indeed, {\sc State-resilience} is undecidable for a Minsky machine $M$ with at least $3$ counters when
$\Safe$ is downward-closed, since it is possible to guarantee that state $q_f(0,0,0)$ is the only $\Safe$ element potentially reachable from $\Bad$.
 As seen in 
Proposition~\ref{indec WSTS with dcs},\alain{la Proposition~\ref{indec WSTS with dcs} n'apparait que dans les annéexes...}
 the sequences of $M$ reaching a $\Safe$ state from a $\Bad$ one can be simulated in a reset-VASS
by sequences reaching a $\Safe'$ state from a $\Bad'$ one,
 and vice versa, hence the following result. 
% \alain{trop rapide}
%\mathieu{tjr trop rapide ?}
%\alain{ça va}

>>>>

\mathieu{Reviewer 1: the example at the bottom of \textbf{ page~\pageref{indec WSTS}}, even if it is a WSTS, is a very particular case [...] wonder if classes containing such  systems are interesting per se. => citer un autre résultat où les increasing recursive functions ont été utilisées ?}

@@

We now consider the case $\Safe = \mathop{\downarrow} \Safe$.
%
Unfortunately {\sc State-resilience} is undecidable in this case. As for {\sc Resilience} in WSTS when $\Safe = \mathop{\downarrow} \Safe$, this stems from undeciability of the corresponding problem in Minsky machines.
Indeed, {\sc State-resilience} is undecidable for a Minsky machine $M$ with at least $3$ counters when
$\Safe$ is downward-closed, since it is possible to guarantee that state $q_f(0,0,0)$ is the only $\Safe$ element potentially reachable from $\Bad$.
 As seen in 
Proposition~\ref{indec WSTS with dcs},\alain{la Proposition~\ref{indec WSTS with dcs} n'apparait que dans les annéexes...}
\mathieu{Elle apparaît dans le corps du texte aussi mais j'avais utilisé deux fois le même label ce qui est corrigé maintenant.}
 the sequences of $M$ reaching a $\Safe$ state from a $\Bad$ one can be simulated in a reset-VASS
by sequences reaching a $\Safe'$ state from a $\Bad'$ one,
 and vice versa, hence the following result. 
% \alain{trop rapide}
%\mathieu{tjr trop rapide ?}
%\alain{ça va}
